\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-23 chapters/0_abstract.tex
Add Anna's comments on intro

% !TEX root = ../agglo_clust_review.tex
%%%%%%%%% ABSTRACT
\begin{abstract}
We propose a novel theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and cannot-link constraints. We prove how these different combinations correspond to existing clustering methods as well as new algorithms that we introduce and analyze. An extensive comparison study is performed to evaluate properties of the clustering algorithms, e.g. robustness and efficiency, by applying them to instance segmentation, which is the task of partitioning an image into distinct segments. We show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and the CityScapes dataset. 
\end{abstract}

>>>>

% !TEX root = ../agglo_clust_review.tex
%%%%%%%%% ABSTRACT
\begin{abstract}
We propose a novel theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and cannot-link constraints. We prove the equivalence of the existing clustering methods to some of those combinations and introduce new algorithms for combinations which have not been studied yet. An extensive comparison is performed to evaluate properties of the clustering algorithms, e.g. robustness and efficiency, by applying them to the problem of instance segmentation in images. We show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and on the CityScapes dataset. 
\end{abstract}

### 2019-05-23 chapters/1_intro.tex
Add Anna's comments on intro

\section{Introduction}
In computer vision, the clustering of weighted graphs has been successfully applied to such tasks as image segmentation, object tracking and pose estimation. %image segmentation, object tracking, stereo matching, etc.), to high-level tasks (e.g. image classification, object recognition, image parsing
% to model many types of re- lations and processes in physical, biological, social and information systems
Most graph clustering methods work with positive edge weights only, which can be interpreted as similarities or distances between the nodes. These methods are parameter-based and require users to specify the desired numbers of clusters or a termination criterion (e.g. spectral clustering or iterated normalized cuts) or even a supervision in terms of seeds (e.g. seeded watershed or random walker).  
%Hierarchical clustering is a popular graph clustering method, which creates a hierarchy of clusters. Hierarchical agglomerative clustering (HAC) is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}. This method usually requires the user to choose a level in the cluster hierarchy defining the desired output clustering.

Other graph clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between nodes. The advantage of using signed graphs over positive-weighted graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters. This can be done optimally by solving the so-called \emph{multicut optimization} or \emph{correlation clustering} problem \cite{kappes2011globally,chopra1991multiway}. However, this problem is NP-hard, so instead of finding optimal solutions, several greedy agglomerative clustering algorithms have been proposed. 
% Some of these methods \cite{levinkov2017comparative,wolf2018mutex} dynamically introduce cannot-link constraints, representing mutual exclusion relationships between clusters.

Thus, agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter free and efficient. Despite the fact that there exists a variety of these algorithms \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}, there have been no overarching studies comparing them and making it possible to choose the most appropriate algorithm for particular applications and assess their properties, e.g. robustness and efficiency.

@@

In this paper, we propose a novel theoretical framework for generalizing over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering, which is a popular bottom-up approach defining an hierarchy of clusters on positive-weighted graphs \cite{lance1967general}. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}. %, i.e. mutual exclusion between clusters. 
We then theoretically prove that different combinations correspond to existing clustering algorithms as well as new algorithms that we introduce and explore. % The framework can also be easily expended to accommodate additional linkage criteria.
%As a first contribution, we reformulate several of these recently proposed graph agglomerative algorithms in a simple review framework (Sec. \ref{sec:general_framework}) that represents a generalization of agglomerative HC to graphs with both attractive and repulsive edge weights (see Figure \ref{fig:intro_figure} for a visual abstract). From this new point of view, agglomerative HC and algorithms proposed in \cite{levinkov2017comparative,wolf2018mutex,lance1967general,kardoostsolving} all share a general procedure but differ in the way inter-cluster interaction is updated after each iteration (Table \ref{tab:linkage-criteria}). At the same time, we also show that this framework allows us to introduce totally new variations of these algorithms. 
%Ultimately, by presenting this simple general approach, our hope is to motivate a deeper understanding of the connection between algorithms for unsigned and signed graphs.

We evaluate and compare these algorithms on \emph{instance segmentation}, which is a computer vision task consisting in assigning each pixel of an image to an object instance. %, where the number of instances is usually not known in advance. 
We use a CNN to predict the edge weights of a graph such that each node represents a pixel of the image, similarly to \cite{liu2018affinity,lee2017superhuman,wolf2018mutex}, and provide these weights as input to the algorithms in our framework (see Fig. \ref{fig:intro_figure}). 
% For our experiments, we focus on a \emph{proposal-free} deep learning method that does not involve object detection but directly group pixels into object instances. 
%  (for example in electron microscopy (EM) image volumes of neurons \cite{arganda2015crowdsourcing})

With our comparison experiments, performed both on 2D urban scenes and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
Our findings show that one of the new agglomerative algorithms introduced by our generalized framework, based on an average linkage criterion, consistently outperforms all other previously known agglomerative algorithms for signed graphs and achieves competitive scores on the challenging CREMI 2016 segmentation benchmark.
% This simple agglomerative algorithm also achieves competitive scores on the challenging CREMI 2016 segmentation benchmark, similarly to other approaches that rely on complex multi-step pipelines.

>>>>

\section{Introduction}
In computer vision, the clustering of weighted graphs has been successfully applied to such tasks as image segmentation, object tracking and pose estimation. %image segmentation, object tracking, stereo matching, etc.), to high-level tasks (e.g. image classification, object recognition, image parsing
% to model many types of re- lations and processes in physical, biological, social and information systems
Most graph clustering methods work with positive edge weights only, which can be interpreted as similarities or distances between the nodes. These methods are parameter-based and require users to specify the desired numbers of clusters or a termination criterion (e.g. spectral clustering or iterated normalized cuts) or even to add a seed for each object  (e.g. seeded watershed or random walker).  
%Hierarchical clustering is a popular graph clustering method, which creates a hierarchy of clusters. Hierarchical agglomerative clustering (HAC) is a bottom-up approach starting with each node assigned to its own cluster and incrementally merging clusters while moving up the hierarchy \cite{lance1967general}. This method usually requires the user to choose a level in the cluster hierarchy defining the desired output clustering.

Other graph clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between nodes. The advantage of signed graphs over positive-weighted graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters. This can be done optimally by solving the so-called \emph{multicut optimization} or \emph{correlation clustering} problem \cite{kappes2011globally,chopra1991multiway}. This problem is NP-hard, but approximate solvers have already been proposed \cite{beier2016efficient}. Besides, the general problem of graph partitioning can be solved approximately by greedy agglomerative clustering \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}.

Agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter-free and efficient. Despite the fact that there exists a variety of these algorithms, no overarching study has so far been made to compare their robustness and efficiency or to provide guidelines for matching an algorithm to the partitioning problem at hand.

@@

In this paper, we propose a novel theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering on positive-weighted graphs \cite{lance1967general}. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}. %, i.e. mutual exclusion between clusters. 
We then formally prove that some of the combinations correspond to existing clustering algorithms and introduce new algorithms for combinations which have not been explored yet. % The framework can also be easily expended to accommodate additional linkage criteria.
%As a first contribution, we reformulate several of these recently proposed graph agglomerative algorithms in a simple review framework (Sec. \ref{sec:general_framework}) that represents a generalization of agglomerative HC to graphs with both attractive and repulsive edge weights (see Figure \ref{fig:intro_figure} for a visual abstract). From this new point of view, agglomerative HC and algorithms proposed in \cite{levinkov2017comparative,wolf2018mutex,lance1967general,kardoostsolving} all share a general procedure but differ in the way inter-cluster interaction is updated after each iteration (Table \ref{tab:linkage-criteria}). At the same time, we also show that this framework allows us to introduce totally new variations of these algorithms. 
%Ultimately, by presenting this simple general approach, our hope is to motivate a deeper understanding of the connection between algorithms for unsigned and signed graphs.

We evaluate and compare these algorithms on \emph{instance segmentation} - a computer vision task of assigning each pixel of an image to an object instance. %, where the number of instances is usually not known in advance. 
We use a CNN to predict the edge weights of a graph such that each node represents a pixel of the image, similarly to \cite{liu2018affinity,lee2017superhuman,wolf2018mutex}, and provide these weights as input to the algorithms in our framework (see Fig. \ref{fig:intro_figure}). 
% For our experiments, we focus on a \emph{proposal-free} deep learning method that does not involve object detection but directly group pixels into object instances. 
%  (for example in electron microscopy (EM) image volumes of neurons \cite{arganda2015crowdsourcing})

With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
Our findings show that one of the new agglomerative algorithms introduced by our generalized framework, based on an average linkage criterion, consistently outperforms all other previously known agglomerative algorithms for signed graphs and achieves competitive scores on the challenging CREMI 2016 segmentation benchmark.
% This simple agglomerative algorithm also achieves competitive scores on the challenging CREMI 2016 segmentation benchmark, similarly to other approaches that rely on complex multi-step pipelines.
